### 2014-03-29 ms_probaweb.tex
1. Added a reference to the bibtex file 2. Some work on the definition of the metaweb

The metaweb concept is making its way through the network litterature even
though it has never been formally and technically defined. It is usually
conceived as a network of interactions among species that could potentially
co-occur. It is usually represented by a binary matrix and thus
deterministically. Here we define it as the matrix of interaction probabilities
between co-occurring species. It thus represents potential interactions and
should therefore include interactions between species that never co-occurred but
are susceptible to. The problem with most representations of metawebs to date is
that the effect of co-occurrence is never factored out. The traditional approach
to build a metaweb is to cumulate observations across replicated networks. The
main problem with that approach is that the co-occurrence of rare species is
extremely unlikely and thus most often appear as an absence of interactions in
the metaweb. This approach is inappropriate because the observed co-occurrence
will have a strong signature on the evaluation of interactions. A rarefaction
analysis previously shown that interactions accumulate with the addition of
networks at a slower rate than species richness. It indicates that it is harder
to have a direct evaluation of interactions from observeration than it is to
evaluate species richness. If built from the observation of interactions, then
the only way to fill a metaweb is by running cafeteria experiments between all
pairs of species. Otherwise, the metaweb should be inferred using traits and
phylogenetic information. Most of the published metawebs are therefore
incomplete because of their sensitivity to sampling heterogeneity. We will come
back to the issue of evaluating the metaweb in the sections Example and Applications

>>>>

% The following paragraph
% (1) is too long -- I tried to cut some of it, up to half of it
% (2) comes at an awkward moment -- this is the key issue we try to solve, it should be in the introduction

The metaweb concept is making its way through the network litterature even
though it has never been formally and technically defined.
% Yes, but no. All of the people that ever wrote the word "metaweb" are authors on this paper.
It is usually conceived as a network of interactions among species
that could potentially co-occur, and represented by a binary matrix,
\emph{i.e.} a probabilistic matrix in which the probability of observing
an interaction is either 0 or 1. As the metaweb is usually constructed by
aggregating observations, it assigns a probability of 0 to the interaction
of species that never co-occurred, and is unable to factor-out the effect of
co-occurrence. The main problem with that approach is that the co-occurrence
of rare species is extremely unlikely and thus most often appear as an absence
of interactions in the metaweb. This approach is inappropriate because the
observed co-occurrence will have a strong signature on the evaluation of
interactions. A rarefaction analysis previously shown that interactions
accumulate with the addition of networks at a slower rate than species
richness \parencite{Poisot2012d}. It indicates that it is harder to have a
direct evaluation of interactions from observeration than it is to evaluate
species richness. If built from the observation of interactions, then the
only way to fill a metaweb is by running cafeteria experiments between all
pairs of species. Otherwise, the metaweb should be inferred using traits
and phylogenetic information. Most of the published metawebs are therefore
incomplete because of their sensitivity to sampling heterogeneity. We will
come back to the issue of evaluating the metaweb in the sections Applications.
